The Use of Quantum Computing\\ in Algorithmic Trading

### 2025-01-06 Documents/Article/article.tex

From the results, it is clear that the \textit{Buy and Keep Trader} strategy performs the best under the PCA model, followed by the \textit{Remain Value Trader} with a 100\% allocation. The portfolio value for these traders steadily increases, reflecting the overall market trends captured by the PCA model. In contrast, the SVM model fails to provide any meaningful predictions for portfolio growth, as evidenced by the flat portfolio value for all trader types. This suggests that SVM is unsuitable for modeling financial market predictions in this context.

@@

These findings suggest that while PCA remains the most effective model for predicting stock prices and simulating trading strategies, the potential of quantum algorithms is not yet fully realized in this domain. The PCA model’s ability to capture market trends translates into better decision-making for traders, especially for strategies such as Remain Value Trading. This strategy benefits the most from PCA’s accuracy in tracking long-term market movements, ensuring consistent growth in portfolio value over time. However, it is worth noting that SVM occasionally demonstrates strong predictive performance, indicating that it may have untapped potential in certain market conditions or specific scenarios.

>>>>

From the results, it is clear that the \textit{Buy and Keep Trader} strategy performs the best under the PCA model, followed by the \textit{Remain Value Trader} with a 100\% allocation. The portfolio value for these traders steadily increases, reflecting the overall market trends captured by the PCA model. In contrast, in most scenarios the SVM model fails to provide any meaningful predictions for portfolio growth, as evidenced by the flat portfolio value for all trader types. However, it is worth noting that SVM occasionally demonstrates strong predictive performance, indicating that it may have untapped potential in certain market conditions or specific scenarios.

@@
